VM-Centric Snapshot Deduplication for Cloud Data Backup

### 2015-03-07 snapshot_system/mass.tex
re

\documentclass[10pt,reprint]{socc14}

%\documentclass[conference]{IEEEtran}

@@

 \authorinfo{
   Wei Zhang$^{\star,\ast}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  
Hong Tang$^\dagger$\\
   $^\star$University of California at Santa Barbara \ \ \  \\
   $^\ast$Pure Storage Inc.\ \ \  $^\dagger$Alibaba Inc. }
%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com

  %{\normalsize $^\star$University of California at Santa Barbara} \ \ {\normalsize$^\dagger$Alibaba Inc.} \\

\comments{
\author{
\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{1,2}, Daniel Agun\IEEEauthorrefmark{2}, 
Tao Yang\IEEEauthorrefmark{1}, Rich Wolski\IEEEauthorrefmark{1}, 
Hong Tan\IEEEauthorrefmark{3}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}University of California at Santa Barbara}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Pure Storage Inc.}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Alibaba Inc.}
%Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$,
%Xiaogang Li$^\dagger$, and Rachael Zeng$^\dagger$ \\
%   {\normalsize $^\star$UC Santa Barbara}\\
%   {\normalsize$^\dagger$Alibaba.com}
}
}
\maketitle

@@

%\linespread{.97} % to squeeeze lines and put figures in same page
%\appendix
\bibliographystyle{abbrvnat}
\bibliography{library,dedup1}
\end{document}

>>>>

%\documentclass[10pt,reprint]{socc14}

\documentclass[conference]{IEEEtran}

@@

\comments{
 \authorinfo{
   Wei Zhang$^{\star\ast}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  
Hong Tang$^\dagger$\\
   $^\star$University of California at Santa Barbara \ \ \  \\
   $^\ast$Pure Storage Inc.\ \ \  $^\dagger$Alibaba Inc. }
%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com

  %{\normalsize $^\star$University of California at Santa Barbara} \ \ {\normalsize$^\dagger$Alibaba Inc.} \\
}

\author{
\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}, Daniel Agun\IEEEauthorrefmark{2}, 
Tao Yang\IEEEauthorrefmark{1}, Rich Wolski\IEEEauthorrefmark{1}, 
Hong Tan\IEEEauthorrefmark{3}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}University of California at Santa Barbara}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Pure Storage Inc.}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Alibaba Inc.}
%Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$,
%Xiaogang Li$^\dagger$, and Rachael Zeng$^\dagger$ \\
%   {\normalsize $^\star$UC Santa Barbara}\\
%   {\normalsize$^\dagger$Alibaba.com}

}
\maketitle

@@

%\linespread{.97} % to squeeeze lines and put figures in same page
%\appendix
%\bibliographystyle{abbrvnat}
\bibliographystyle{abbrv}
\bibliography{library,dedup1}
\end{document}
